---
title: "R Notebook"
output: html_notebook
---

ISSRE-2018

```{r}
library(plyr)
library(dplyr)
library(reshape)
library(ggplot2)
library(RNeo4j)
library(sqldf)

methods <-
  read.csv(
    "/home/r4ph/R/analysis/methods/5projectsTotalall.csv",
    stringsAsFactors = FALSE
  )
```

```{r}
####General Metrics of Individual Projects
data_changes <- filter(methods, Metric == 'All', groupMetric == 'All', changeType == 'All')

```


```{r}
getTotalChanges <- function (x) {
  Reduce("+",as.integer(strsplit(x, ",")[[1]]))
}

getTotalBugs <- function (x) {
  as.integer(length(as.list(strsplit(x, ","))[[1]]))
}

data_changes[,"Changes"] <- mapply(getTotalChanges, data_changes$elementsValue)
data_changes[,"totalofBugs"] <- mapply(getTotalBugs, data_changes$IDbugs)


  
```

### (G1)To investigate the occurrence of commits along the history; 
####(Q1.1) How often are commits performed? 
```{r}

data_plot <- data_changes %>%
  group_by(Project, NtimeofCommits) %>%
  summarise(Changes = sum(Count)) %>%
  mutate(Percentual = Changes / sum(Changes) * 100) %>%
  ungroup()

data_plot

plot1 <- ggplot(filter(data_plot, NtimeofCommits <= 10)) +
  geom_bar(aes(x=NtimeofCommits,y=Percentual,group=Project), position = "dodge", stat = "identity")+
  facet_grid(.~Project,scales="free") + 
  theme(legend.position= c(0.7, 0.95), legend.direction="horizontal", legend.title = element_blank(), 
        legend.text=element_text(size=5), legend.background = element_rect(fill = "transparent", colour = NA) ) +
  ylab("Percentual of Time Series by Commits") + scale_x_discrete(name ="Number of Commits", limits=c("1","2","3","4","5","6","7","8","9","10")) +
  theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),
        plot.background = element_rect(fill = "transparent", colour = NA))


plot1
```



####(Q1.2) How disperse are changes among time series? (Changes x Commits)
```{r}

data_plot <- data_changes %>%
  group_by(Project, NtimeofCommits) %>%
  summarise(Changes = sum(Changes)) %>%
  mutate(Percentual = Changes / sum(Changes) * 100) %>%
  ungroup()

data_plot

for (project in projects){
  plot2 <- ggplot(filter(data_plot, Project == project, NtimeofCommits <= 25)) +
  geom_bar(aes(x=NtimeofCommits,y=Percentual), position = "dodge", stat = "identity")+
  facet_grid(.~Project,scales="free") + 
  theme(legend.position= c(0.7, 0.95), legend.direction="horizontal", legend.title = element_blank(), 
        legend.text=element_text(size=5), legend.background = element_rect(fill = "transparent", colour = NA)) +
  ylab("Percentual of Changes by Commits") + scale_x_discrete(name ="Number of Commits", limits=seq(1,25)) +
  theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),
        plot.background = element_rect(fill = "transparent", colour = NA))

  print(plot2)
}

```

####(Q1.3) How disperse are changes among commits? (Changes x Time Series)
```{r}

data_plot <- data_changes %>%
    dplyr::group_by(Project, NtimeofCommits) %>%
    dplyr::summarise(nTs = sum(Count), 
                    nChanges = sum(Changes),
                    ChangesByTs = sum(Changes)/ sum(Count),
                    nBugs = sum(totalofBugs)) %>%
    dplyr::mutate(Percentual = (ChangesByTs/sum(ChangesByTs)) * 100 ) %>%
    dplyr::ungroup()

data_plot

for (project in projects){
  
  plot2 <- ggplot(filter(data_plot, Project == project, NtimeofCommits <= 25)) +
  geom_bar(aes(x=NtimeofCommits,y=Percentual), position = "dodge", stat = "identity")+
  facet_grid(.~Project,scales="free") + 
  theme(legend.position= c(0.7, 0.95), legend.direction="horizontal", legend.title = element_blank(), 
        legend.text=element_text(size=5), legend.background = element_rect(fill = "transparent", colour = NA)) +
  ylab("Percentual of Changes by Time Seris") + scale_x_discrete(name ="Number of Commits", limits=seq(1,25)) +
  theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),
        plot.background = element_rect(fill = "transparent", colour = NA))

  print(plot2)
}


```

### (G2)To assess the introduction of bugs along the history; 

```{r}
data_plot <- data_changes %>%
    dplyr::group_by(Project, NtimeofCommits) %>%
    dplyr::summarise(nTs = sum(Count), 
                    nChanges = sum(Changes),
                    nBugs = sum(totalofBugs),
                    BugsByTs = sum(totalofBugs)/sum(Count),
                    BugsByChanges = sum(totalofBugs)/ sum(Changes)) %>%
    dplyr::mutate(PercBugsByTs = (BugsByTs/sum(BugsByTs)) * 100,
                  PercBugsByCommit = (nBugs/sum(nBugs)) * 100,
                  PercBugsByChanges = (BugsByChanges/sum(BugsByChanges)) * 100) %>%
    dplyr::ungroup()

data_plot
```

#### (Q2.1) How often are bugs introduced among the time series? (Bugs x Time Series)
```{r}

for (project in projects){
  
  plot2 <- ggplot(filter(data_plot, Project == project, NtimeofCommits <= 25)) +
  geom_bar(aes(x=NtimeofCommits,y=PercBugsByTs), position = "dodge", stat = "identity")+
  facet_grid(.~Project,scales="free") + 
  theme(legend.position= c(0.7, 0.95), legend.direction="horizontal", legend.title = element_blank(), 
        legend.text=element_text(size=5), legend.background = element_rect(fill = "transparent", colour = NA)) +
  ylab("Percentual of Changes by Time Seris") + scale_x_discrete(name ="Number of Commits", limits=seq(1,25)) +
  theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),
        plot.background = element_rect(fill = "transparent", colour = NA))

  print(plot2)
}

```

#### (Q2.2) How often are bugs introduced among the commits? (Bugs x Commits)
```{r}

for (project in projects){
  
  plot2 <- ggplot(filter(data_plot, Project == project, NtimeofCommits <= 25)) +
  geom_bar(aes(x=NtimeofCommits,y=PercBugsByCommit), position = "dodge", stat = "identity")+
  facet_grid(.~Project,scales="free") + 
  theme(legend.position= c(0.7, 0.95), legend.direction="horizontal", legend.title = element_blank(), 
        legend.text=element_text(size=5), legend.background = element_rect(fill = "transparent", colour = NA)) +
  ylab("Percentual of Changes by Time Seris") + scale_x_discrete(name ="Number of Commits", limits=seq(1,25)) +
  theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),
        plot.background = element_rect(fill = "transparent", colour = NA))

  print(plot2)
}

```

#### (Q2.3) How often are bugs introduced among the changes? (Bugs x CHanges)
```{r}

for (project in projects){
  
  plot2 <- ggplot(filter(data_plot, Project == project, NtimeofCommits <= 25)) +
  geom_bar(aes(x=NtimeofCommits,y=PercBugsByChanges), position = "dodge", stat = "identity")+
  facet_grid(.~Project,scales="free") + 
  theme(legend.position= c(0.7, 0.95), legend.direction="horizontal", legend.title = element_blank(), 
        legend.text=element_text(size=5), legend.background = element_rect(fill = "transparent", colour = NA)) +
  ylab("Percentual of Changes by Time Seris") + scale_x_discrete(name ="Number of Commits", limits=seq(1,25)) +
  theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),
        plot.background = element_rect(fill = "transparent", colour = NA))

  print(plot2)
}

```

