---
title: "R Notebook"
output: html_notebook
---


```{r}

library(dplyr)
library(stringr)
library(ggplot2)
library(ggpubr)
library(sqldf)

methods <-
  read.csv(
    "~/R/analysis/insertions/insertionsall.csv",
    stringsAsFactors = FALSE
  )

chunkIt <- function (seq, avg) {
  out = list()
  last = 0.0
  i<- 0
  while (last < length(seq)){
    i <- i+ 1
    out[[i]] <- seq[(as.integer(last)+1):as.integer(last + avg)]
    last = last + avg
  }
  
  return (out)
}

# implementing the function:
ggpareto <- function(x, title) {
  
  #title <- deparse(substitute(x))
  
  x <- data.frame(modality = na.omit(x))
  
  Df <- x %>% group_by(modality) %>% summarise(frequency=n()) %>% 
    arrange(desc(frequency))
  
  Df$modality <- ordered(Df$modality, levels = unlist(Df$modality, use.names = F))
  
  Df <- Df %>% mutate(modality_int = as.integer(modality), 
                      cumfreq = cumsum(frequency), cumperc = cumfreq/nrow(x) * 100)
  nr <- nrow(Df)
  N <- sum(Df$frequency)
  
  Df_ticks <- data.frame(xtick0 = rep(nr +.55, 11), xtick1 = rep(nr +.59, 11), 
                         ytick = seq(0, N, N/10))
  
  y2 <- c("  0%", " 10%", " 20%", " 30%", " 40%", " 50%", " 60%", " 70%", " 80%", " 90%", "100%")
  
  g <- ggplot(Df, aes(x=modality, y=frequency)) + 
    geom_bar(stat="identity", aes(fill = modality_int)) +
    geom_line(aes(x=modality_int, y = cumfreq, color = modality_int)) +
    geom_point(aes(x=modality_int, y = cumfreq, color = modality_int), pch = 19) +
    scale_y_continuous(breaks=seq(0, N, N/10), limits=c(-.02 * N, N * 1.02)) + 
    scale_x_discrete(breaks = Df$modality) +
    guides(fill = FALSE, color = FALSE) + 
    annotate("rect", xmin = nr + .55, xmax = nr + 1, 
             ymin = -.02 * N, ymax = N * 1.02, fill = "white") +
    annotate("text", x = nr + .8, y = seq(0, N, N/10), label = y2, size = 3.5) +
    geom_segment(x = nr + .55, xend = nr + .55, y = -.02 * N, yend = N * 1.02, color = "grey50") +
    geom_segment(data = Df_ticks, aes(x = xtick0, y = ytick, xend = xtick1, yend = ytick)) +
    labs(title = paste0("Pareto Chart of ", title), y = "Frequency of Methods With Bugs", x = "Metrics") +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
  
  print(g)
  
  #return(list(graph = g, Df = Df[, c(3, 1, 2, 4, 5)]))
  return (graph = g)
}

# The palette with black:
cbPalette <- c("#F15854", "#5DA5DA", "#FAA43A", "#B276B2", "#4D4D4D", "#009E73", "#F17CB0", "#DECF3F")

projects <- unique(methods$Project)

```

###RQ1: How often do changes and bugs occurin the history of methods?


#### :

```{r}
data_total <-
  read.csv(
    "/home/r4ph/R/analysis/methods/5projectsTotalall.csv",
    stringsAsFactors = FALSE
)

resultsP1P5 <-
  sqldf(
    "SELECT Project, SUM(Count) as TotalTimeSeries, 
     SUM(CASE WHEN (P1 = 1)  THEN 1 ELSE 0 end) as 'C1',
     SUM(CASE WHEN (P1 = 1) AND (P4 = 1) THEN 1 ELSE 0 end) as 'C1-C2',
     SUM(CASE WHEN (P1 = 1) AND (P4 = 1) AND (P5 = 1) THEN 1 ELSE 0 end) as 'C1-C2-C3',
     SUM(CASE WHEN (P1 = 1) AND (P4 = 1) AND (P3 = 1) THEN 1 ELSE 0 end) as 'C1-C2-C4',
     SUM(CASE WHEN (P1 = 1) AND (P4 = 1) AND (P3 = 1) AND (P5 = 1) THEN 1 ELSE 0 end) as 'C1-C2-C3-C4'
     FROM data_total
     GROUP BY Project"
  )

resultsP1P5

#Join Regression With Df

```


####General Metrics of Individual Projects

```{r}
data_plot <- filter(methods, Metric == 'All', groupMetric == 'All', changeType == 'All', groupMetric != "RM")

data_plot <- data_plot %>%
  group_by(Project, NtimeofCommits) %>%
  summarise(Changes = sum(Count)) %>%
  mutate(Percentual = Changes / sum(Changes) * 100) %>%
  ungroup()

plot1 <- ggplot(filter(data_plot, NtimeofCommits <= 10, Project %in% projects[0:5])) +
  geom_bar(aes(x=NtimeofCommits,y=Percentual,group=Project), position = "dodge", stat = "identity")+
  facet_grid(.~Project,scales="free") + 
  theme(legend.position= c(0.7, 0.95), legend.direction="horizontal", legend.title = element_blank(), 
        legend.text=element_text(size=5), legend.background = element_rect(fill = "transparent", colour = NA) ) +
  ylab("Percentual") + scale_x_discrete(name ="Number of Commits", limits=c("1","2","3","4","5","6","7","8","9","10")) +
  theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),
        plot.background = element_rect(fill = "transparent", colour = NA))


plot1

# plot2 <- ggplot(filter(data_plot, NtimeofCommits <= 10, Project %in% projects[6:10])) +
#   geom_bar(aes(x=NtimeofCommits,y=Percentual,group=Project), position = "dodge", stat = "identity")+
#   facet_grid(.~Project,scales="free") +
#   theme(legend.position= c(0.7, 0.95), legend.direction="horizontal", legend.title = element_blank(),
#         legend.text=element_text(size=5), legend.background = element_rect(fill = "transparent", colour = NA) ) +
#   ylab("Percentual") + scale_x_discrete(name ="Number of Commits", limits=c("1","2","3","4","5","6","7","8","9","10")) +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         plot.background = element_rect(fill = "transparent", colour = NA))
# 
# ggarrange(plot1 , plot2 , ncol = 1, nrow = 2)
```




#### Add/Del Metrics of Individual Projects

```{r}

data_plot <- filter(methods, Metric == 'All', groupMetric == 'All', changeType != 'All', groupMetric != "RM")

data_plot <- data_plot %>%
  group_by(Project, changeType, NtimeofCommits) %>%
  summarise(Changes = sum(Count)) %>%
  mutate(Percentual = Changes / sum(Changes) * 100) %>%
  ungroup()

for (change in unique(data_plot$changeType)){
  
  ##Add/Del Changes
  plot1 <- ggplot(filter(data_plot, NtimeofCommits <= 10, Project %in% projects[0:5], changeType == change)) +
    geom_bar(aes(x=NtimeofCommits,y=Percentual,group=Project), position = "dodge", stat = "identity")+
    facet_grid(.~Project,scales="free") + 
    theme(legend.position= c(0.7, 0.95), legend.direction="horizontal", legend.title = element_blank(), 
          legend.text=element_text(size=5), legend.background = element_rect(fill = "transparent", colour = NA) ) +
    ylab("Percentual") + scale_x_discrete(name ="Number of Commits", limits=c("1","2","3","4","5","6","7","8","9","10")) +
    theme(panel.grid.minor = element_blank(), 
          panel.grid.major = element_blank(),
          plot.background = element_rect(fill = "transparent", colour = NA))+
    labs(title = paste0("Barplots of changes by ", change))
  
  print(plot1)
  
  # plot2 <- ggplot(filter(data_plot, NtimeofCommits <= 10, Project %in% projects[6:10], changeType == change)) +
  #   geom_bar(aes(x=NtimeofCommits,y=Percentual,group=Project), position = "dodge", stat = "identity")+
  #   facet_grid(.~Project,scales="free") + 
  #   theme(legend.position= c(0.7, 0.95), legend.direction="horizontal", legend.title = element_blank(), 
  #         legend.text=element_text(size=5), legend.background = element_rect(fill = "transparent", colour = NA) ) +
  #   ylab("Percentual") + scale_x_discrete(name ="Number of Commits", limits=c("1","2","3","4","5","6","7","8","9","10")) +
  #   theme(panel.grid.minor = element_blank(), 
  #         panel.grid.major = element_blank(),
  #         plot.background = element_rect(fill = "transparent", colour = NA))
  # 
  # print(ggarrange(plot1 , plot2 , ncol = 1, nrow = 2))
  
}
```

####Groups Metrics of All Projects

```{r message=FALSE, warning=FALSE, echo=FALSE, comment= FALSE, results=FALSE}
data_plot <- filter(methods, Metric == 'All',  groupMetric != 'All', changeType == 'All', groupMetric != "RM")

data_plot <- data_plot %>%
  group_by(groupMetric, NtimeofCommits) %>%
  summarise(Changes = sum(Count)) %>%
  mutate(Percentual = Changes / sum(Changes) * 100) %>%
  ungroup()

list_plots <- list()
z <- 0

#for (i in 1:length(projects)){
#group_metrics <- unique(filter(data_plot, Project == projects[i])$groupMetric)
#list_groups <- chunkIt(groupsMetrics, 5)

group_metrics <- unique(data_plot$groupMetric)
  
list_groups <- chunkIt(group_metrics, 4)
  
  for (j in 1: length(list_groups)){
    
    list_groups_na <- list_groups[[j]]
    
    plot1 <- ggplot(filter(data_plot, NtimeofCommits <= 10, groupMetric %in% list_groups_na))+ #, Project == projects[i])) +
      geom_bar(aes(x=NtimeofCommits, y=Percentual, group= groupMetric), position = "dodge", stat = "identity") +
      facet_grid(.~groupMetric,scales="free") + scale_x_discrete(name ="Number of Commits", limits=c("1","2","3","4","5","6","7","8","9","10")) +
      theme(legend.position= c(0.7, 0.95), legend.direction="horizontal", legend.title = element_blank(), 
            legend.text=element_text(size=5), legend.background = element_rect(fill = "transparent", colour = NA)) +
      ylab("Percentual") + 
      theme(panel.grid.minor = element_blank(), 
            panel.grid.major = element_blank(),
            plot.background = element_rect(fill = "transparent", colour = NA)) +
      labs(title = paste0("Groups Metrics ", ""))# projects[i]))
    
    z <- z + 1
    list_plots[[z]] <- plot1
  }

#}

#Plots of groups
for (i in 1:length(list_plots)){
  print(list_plots[[i]])
}
```

####Individual Metrics of All Projects

```{r}

data_plot <- filter(methods, Metric != 'All',  groupMetric != 'All', changeType == 'All', groupMetric != "RM")

data_plot <- data_plot %>%
  group_by(Metric, NtimeofCommits) %>%
  summarise(Changes = sum(Count)) %>%
  mutate(Percentual = Changes / sum(Changes) * 100) %>%
  ungroup()

list_plots <- list()
z <- 0

#projects <- unique(data_plot$Project)
#for (i in 1:length(projects)){
# metrics <- unique(filter(data_plot, Project == projects[i])$Metric)

metrics <- unique(data_plot$Metric)
  
list_metrics <- chunkIt(metrics, 5)
  
  for (j in 1: length(list_metrics)){
    
    list_metrics_na <- list_metrics[[j]]
    
    plot1 <- ggplot(filter(data_plot, NtimeofCommits <= 10, Metric %in% list_metrics_na)) + #, Project == projects[i])) +
      geom_bar(aes(x=NtimeofCommits, y=Percentual, group= Metric), position = "dodge", stat = "identity") +
      facet_grid(.~Metric,scales="free") + scale_x_discrete(name ="Number of Commits", limits=c("1","2","3","4","5","6","7","8","9","10")) +
      theme(legend.position= c(0.7, 0.95), legend.direction="horizontal", legend.title = element_blank(), 
            legend.text=element_text(size=5), legend.background = element_rect(fill = "transparent", colour = NA)) +
      ylab("Percentual") + 
      theme(panel.grid.minor = element_blank(), 
            panel.grid.major = element_blank(),
            plot.background = element_rect(fill = "transparent", colour = NA)) +
      labs(title = paste0("Individual Metrics ", "")) #projects[i]))
    
    z <- z + 1
    list_plots[[z]] <- plot1
  }

#}

#Plots of Individual metrics
for (i in 1:length(list_plots)){
  print(list_plots[[i]])
}
```


####Groups Metrics of Individual Projects.

```{r message=FALSE, warning=FALSE, echo=FALSE, comment= FALSE, results=FALSE}
data_plot <- filter(methods, Metric == 'All',  groupMetric != 'All', changeType == 'All', groupMetric != "RM")

data_plot <- data_plot %>%
  group_by(Project, groupMetric, NtimeofCommits) %>%
  summarise(Changes = sum(Count)) %>%
  mutate(Percentual = Changes / sum(Changes) * 100) %>%
  ungroup()

list_plots <- list()
z <- 0

for (i in 1:length(projects)){
  
group_metrics <- unique(filter(data_plot, Project == projects[i])$groupMetric)

list_groups <- chunkIt(group_metrics, 5)
  
for (j in 1: length(list_groups)){
    
    list_groups_na <- list_groups[[j]]
    
    plot1 <- ggplot(filter(data_plot, NtimeofCommits <= 10, groupMetric %in% list_groups_na, Project == projects[i])) +
      geom_bar(aes(x=NtimeofCommits, y=Percentual, group= groupMetric), position = "dodge", stat = "identity") +
      facet_grid(.~groupMetric,scales="free") + scale_x_discrete(name ="Number of Commits", limits=c("1","2","3","4","5","6","7","8","9","10")) +
      theme(legend.position= c(0.7, 0.95), legend.direction="horizontal", legend.title = element_blank(), 
            legend.text=element_text(size=5), legend.background = element_rect(fill = "transparent", colour = NA)) +
      ylab("Percentual") + 
      theme(panel.grid.minor = element_blank(), 
            panel.grid.major = element_blank(),
            plot.background = element_rect(fill = "transparent", colour = NA)) +
      labs(title = paste0("Groups Metrics ", projects[i]))
    
    z <- z + 1
    list_plots[[z]] <- plot1
  }

}

#Plots of groups
for (i in 1:length(list_plots)){
  print(list_plots[[i]])
}
```

####Individual Metrics of Each Especific Project.

```{r}

data_plot <- filter(methods, Metric != 'All',  groupMetric != 'All', changeType == 'All', groupMetric != "RM")

data_plot <- data_plot %>%
  group_by(Project, Metric, NtimeofCommits) %>%
  summarise(Changes = sum(Count)) %>%
  mutate(Percentual = Changes / sum(Changes) * 100) %>%
  ungroup()

list_plots <- list()
z <- 0

projects <- unique(data_plot$Project)

for (i in 1:length(projects)){

  metrics <- unique(filter(data_plot, Project == projects[i])$Metric)
  
  list_metrics <- chunkIt(metrics, 5)
  
  for (j in 1: length(list_metrics)){
    
    list_metrics_na <- list_metrics[[j]]
    
    plot1 <- ggplot(filter(data_plot, NtimeofCommits <= 10, Metric %in% list_metrics_na, Project == projects[i])) +
      geom_bar(aes(x=NtimeofCommits, y=Percentual, group= Metric), position = "dodge", stat = "identity") +
      facet_grid(.~Metric,scales="free") + scale_x_discrete(name ="Number of Commits", limits=c("1","2","3","4","5","6","7","8","9","10")) +
      theme(legend.position= c(0.7, 0.95), legend.direction="horizontal", legend.title = element_blank(), 
            legend.text=element_text(size=5), legend.background = element_rect(fill = "transparent", colour = NA)) +
      ylab("Percentual") + 
      theme(panel.grid.minor = element_blank(), 
            panel.grid.major = element_blank(),
            plot.background = element_rect(fill = "transparent", colour = NA)) +
      labs(title = paste0("Individual Metrics ", projects[i]))
    
    z <- z + 1
    list_plots[[z]] <- plot1
  }

}

#Plots of Individual metrics
for (i in 1:length(list_plots)){
  print(list_plots[[i]])
}
```

####RQ2: How close is the relationship between the history of bugs and changes?

```{r}

reg <-
  read.csv(
    "~/R/analysis/methods/5projectsRegression.csv",
    stringsAsFactors = FALSE
  )


resultsRQ2 <-
  sqldf(
    "SELECT Project, SUM(CASE WHEN (P1 = 1) AND (P4 = 1) AND (P3 = 1) AND (P5 = 1) THEN 1 ELSE 0 end) as 'C1-C2-C3-C4',
        SUM(CASE WHEN (P1 = 1) AND (P4 = 1) AND (P3 = 1) AND (P5 = 1) AND (GrangerPos = 1) THEN 1 ELSE 0 end) as 'GrangerPos'
     FROM data_total
     GROUP BY Project"
  )

#Add Regressions
resultsReg <- 
    sqldf(
    "SELECT Project, SUM(Count) as 'Regression'
     FROM reg
     GROUP BY Project"
  )

results_all <-inner_join(resultsRQ2, resultsReg)#,eff_ind)
                     
results_all

```



#### RQ3: Which kind of changes are mostlyrelated to the bugs insertion?

* Gráfico de Pareto de Metricas Individuais de todos os métodos que possuem bugs (sem as metricas redundantes [RM]):


```{r}
#IndividualMetrics
colMethods <- c("Project", "MethodName", "Metric", "groupMetric", "changeType", "elementsValue", "NtimeofCommits", "Count")

#resultsClasses <- subset( resultsClasses, select = c(colClasses) )
resultsMethods <- subset( methods, select = c(colMethods))

#Filter:D
resultsMethods <- filter(resultsMethods, groupMetric != "RM")

#IndividualMetrics
indMetrics<-
  sqldf(
    "SELECT Project, Metric, SUM(Count) as Changes
    FROM resultsMethods
    WHERE changeType = 'All' 
    AND groupMetric <>'All'
    AND Metric <> 'All'
    GROUP BY Project, Metric"
  )

metrics <- c()
# Applying the function to the pareto function:
for (project in projects){
  df <- filter(indMetrics, Project == project)[,c(2,3)]
  i<-1
  for (x in 1:nrow(df)){
    for (y in 1:df$Changes[x]){
      metrics[i] <- df$Metric[x]
      i <- i + 1
    }
  }
  ggpareto(metrics, project)
}

```


* Gráfico de Pareto de Metricas Individuais de todos os métodos que possuem bugs (sem as metricas redundantes [RM]):
```{r}
#IndividualMetrics
colMethods <- c("Project", "MethodName", "Metric", "groupMetric", "changeType", "elementsValue", "NtimeofCommits", "Count")

#resultsClasses <- subset( resultsClasses, select = c(colClasses) )
resultsMethods <- subset( methods, select = c(colMethods))

#Filter:D
resultsMethods <- filter(resultsMethods, groupMetric != "RM")

#IndividualMetrics
groupMetrics<-
  sqldf(
    "SELECT Project, groupMetric, SUM(Count) as Changes
    FROM resultsMethods
    WHERE changeType = 'All' 
    AND groupMetric <>'All'
    AND Metric = 'All'
    GROUP BY Project, groupMetric"
  )

metrics <- c()
# Applying the function to the pareto function:
for (project in projects){
  df <- filter(groupMetrics, Project == project)[,c(2,3)]
  i<-1
  for (x in 1:nrow(df)){
    for (y in 1:df$Changes[x]){
      metrics[i] <- df$groupMetric[x]
      i <- i + 1
    }
  }
  ggpareto(metrics, project)
}
```


#### RQ4: How efficient are the statistically significant relations to predict bugs?


```{r}
 data_granger <-
   read.csv(
     "/home/r4ph/R/analysis/methods/5ProjectsEffectivenessGranger.csv",
     stringsAsFactors = FALSE
 )

 data_c1c4 <-
   read.csv(
     "/home/r4ph/R/analysis/methods/5ProjectsEffectivenessC1C4.csv",
     stringsAsFactors = FALSE
 )
 
  data_reg <-
   read.csv(
     "/home/r4ph/R/analysis/methods/5ProjectsEffectivenessReg.csv",
     stringsAsFactors = FALSE
 )


data_granger <- filter(data_granger, P1==1, P3 == 1, P4 ==1, P5 ==1)

effe_granger <- as.data.frame(data_granger %>%
                               group_by(Project) %>%
                               summarise(##### -------------------- F-MEasure -----------------########
                               fmeasureGranger = round(median(
                               fmeasure.median, na.rm = TRUE
                               ), 2)))

effe_c1c4 <- as.data.frame(data_c1c4 %>%
                               group_by(Project) %>%
                               summarise(##### -------------------- F-MEasure -----------------########
                               fmeasureC1C4 = round(median(
                               fmeasure.median, na.rm = TRUE
                               ), 2)))

effe_reg <- as.data.frame(data_reg %>%
                               group_by(Project) %>%
                               summarise(##### -------------------- F-MEasure -----------------########
                               fmeasureRegression = round(median(
                               fmeasure.median, na.rm = TRUE
                               ), 2)))


eff_all <- inner_join(inner_join(effe_c1c4, effe_granger),effe_reg)
                     
eff_all

```

#### RQ5: Which kind of changes are mosteffective to predicting bugs?

```{r}
data_granger_type <-
  filter(
    data_granger,
    changeType != "All" ,
    groupMetric == "All" & Metric == "All"
  )

#Filter Groups:
data_granger_group <-
  filter(
    data_granger,
    changeType == "All" ,
    groupMetric != "All",
    Metric == "All"
  )

#Filter Individuals Metrics:
data_granger_ind <-
  filter(
    data_granger,
    changeType == "All" ,
    groupMetric != "All",
    Metric != "All"
  )


eff_type <- as.data.frame(data_granger_type %>%
                          group_by(Project) %>%
                          summarise(##### -------------------- F-MEasure -----------------########
                          fmeasureType = round(median(
                          fmeasure.median, na.rm = TRUE
                          ), 2)))
                                        
eff_group <- as.data.frame(data_granger_group %>%
                            group_by(Project) %>%
                            summarise(##### -------------------- F-MEasure -----------------########
                            fmeasureGroup = round(median(
                            fmeasure.median, na.rm = TRUE
                            ), 2)))

eff_ind <- as.data.frame(data_granger_ind %>%
                          group_by(Project) %>%
                          summarise(##### -------------------- F-MEasure -----------------########
                          fmeasureMetric = round(median(
                          fmeasure.median, na.rm = TRUE
                          ), 2)))

eff_all <-inner_join(inner_join(eff_type, eff_group),eff_ind)

eff_all

```
